\huge Platform for Anomaly Detection in Time-Series

### 2018-10-27 article.tex
Working on draft 3

\begin{figure}
\centering
\includegraphics[width=\textwidth]{Workflow}
\caption{Workflow of the classification process.}
\label{fig:workflow}
\end{figure}

@@

In this section we give short descriptions of the anomaly detection methods present in the platform.

\subsection{Outlier Detection Methods}

@@

One might be able to label if an element is an anomaly by setting global lower and upper bounds. This can be used to detect obvious anomalies such as extreme temperature levels or very high blood pressure.

@@

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{Outlier}
\caption{The upper graphs shows measured values from a process, and the lower figure is the classification. While the signal stays withing a certain range of the model, represented here by the upper and lower bounds, the signal is considered nominal. Points that are outside this ``band of normality'' are considered anomalies.}
\label{fig:outlier}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{ChangePoint}   
\caption{In the top most graph, we can see the observed process. In this case it is a pure sine wave. In the middle graphs we can see the coefficient of the model, which in this case is just a function of it's frequency, since it is enough to perfectly describe the process. We consider as anomaly either the change point, either all the points where the model is outside some bounds.}
\label{fig:changepoint}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{Workflow}
\caption{Workflow of the classification process.}
\label{fig:workflow}
\end{figure}

@@

In this section we give short descriptions of some of the possible anomaly types. For each anomaly type we present some methods for detecting such an anomaly.

\subsection{Outliers}

@@

\subsubsection{Bounded Method}

One might be able to label elements as anomalies by setting global lower and upper bounds. This can be used to detect obvious anomalies such as extreme temperature levels or very high blood pressure.

\subsubsection{Model Distance Method}

@@

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{Outlier}
\caption{The upper graphs shows measured values from a process, and the lower figure is the classification. While the signal stays withing a certain range of the model, represented here by the upper and lower bounds, the signal is considered nominal. Points that are outside this ``band of normality'' are considered anomalies.}
\label{fig:outlier}
\end{figure}

\subsubsection{Linear Approximation Method}

\subsubsection{Autoregressive Method}

@@

@@

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{ChangePoint}   
\caption{In the top most graph, we can see the observed process. In this case it is a pure sine wave. In the middle graphs we can see the coefficient of the model, which in this case is just a function of it's frequency, since it is enough to perfectly describe the process. We consider as anomaly either the change point, either all the points where the model is outside some bounds.}
\label{fig:changepoint}
\end{figure}
